Reporte de inventario de eviencias

### 2021-10-30 Latex/journal_v2/research plan/main.tex
add research plan

\textbf{\Large Research Plan} \\
\vspace{10mm}
\textbf{Department of Electrical and Computer Engineering}\\
\vspace{20mm}
{\large University of Oulu}\\
\vspace{20mm}
\end{center}
\vspace{10mm}
{\scriptsize Provisional title:}\\
Dynamic Resource Allocation in O-RAN Architecture using Network Slicing\\

@@

{\scriptsize Supervisor name:}\\
Dr. Onel Lopez\\
\vspace{3mm}

@@

\subsection{Main Contributions}
In this research, as depicted in Figure \ref{fig:c11}, we aim at solving the problem of dynamic network slicing in the O-RAN system. 
Here, we study a single-cell downlink situation involving multiple network slices that share existing radio sources.
The main contributions of
this research are summarized as follow:
\begin{itemize}
\item 
The system has a two-time scale and should be solved in two layers. On a large-time scale, the problem of obtaining an optimal number of VNFs and the VNF placement is performed. Also, the assignment of PRB to the slices is obtained. On a small-time scale, the problem of power allocation, O-RU association and the assignment of PRB to UE in each slice is applied.
\item 
We consider three types of services that requires specific QoS: URLLC, which requires low latency and high reliability; eMBB, which needs high data rate; and mMTC, , which demand short-packet connectivity support for a massive number of low-power devices.
The problem of RAN slicing for different types of services is studied in this research.

@@

In addition, there are $R$ multi-antenna RU that are shared between slices. Each RU $r \in \{1,2,...,R \}$
has $J$ antenna for transmitting and receiving data. Moreover, all RUs, have access to PRBs.
\subsection{The Achievable Rate}
The SNR of $i^{th}$ UE requesting served at slice $s$ on PRB $k$ is obtained from
\begin{equation}\label{eq2}
\rho_{r,u(s,i)}^{k} =  \frac{|p_{r,u(s,i)}^{k}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2}{BN_0 + I_{r,u(s,i)}^{k}},
\end{equation} 
where $p_{r,u(s,i)}^{k}$ represents the transmission power from O-RU $r$ to $i^{th}$ UE served at slice $s$ on PRB $k$. 
${\bold{h}_{r,u(s,i)}^{k}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
$r^{th}$ RU to the $i^{th}$ UE in $s^{th}$ slice. In addition, $\bold{w}_{r,u(s,i)}^{k} \in \mathbb{C}^{J}$ depicts the  transmit beamforming vector from $r^{th}$ RU to the $i^{th}$ UE in $s^{th}$ slice that is the zero forcing beamforming vector to minimize the interference which is indicated as below
\begin{equation}
\bold{w}_{r,u(s,i)}^{k} = {\bold{h}_{r,u(s,i)}^{k}}({\bold{h}_{r,u(s,i)}^{H \: k}} {\bold{h}_{r,u(s,i)}^{k}})^{-1}
\end{equation}
Moreover, $g_{u(s,i)}^r \in \{0,1\}$ is a binary variable that illustrates whether RU $r$ is mapped to the $i^{th}$ UE allocated to $s^{th}$ slice or not. 
Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u(s,i)}^{k}$ is the power of interfering signals represented as follow
\begin{equation}\label{eqI}
\begin{split}
I_{r,u(s,i)}^{k} &=
 \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} \gamma_{1}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}\\
&+ \underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} \gamma_{2}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
\end{split}
\end{equation}
where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
$e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU.

@@

\mathcal{R}_{u(s_1,i)}^{e} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{e,r} 

@@

\mathcal{R}_{u(s_2,i)}^{\mathfrak{u},r} &= \sum_{k=1}^{K_{s_2}} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_2,i)}^{k}){\beta}_{u(s_2,i)}^{k}, \quad \mathfrak{u} \in  \{u,m\} \\
\mathcal{R}_{u(s_1,i)}^{\mathfrak{u}} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_2,i)}^{e,r} 

@@

So, we assume that the total delay is approximate to the processing delay.

@@

T^{\text{\text{tot}}} \approx T^{\text{proc}}

@@

    \end{cases}       

@@

\phi_{s} = M_s^u \phi_s^u + M_s^c \phi_s^c+ M_s^d \phi_s^d

@@

\subsection{Proposed Algorithm and Numerical Results}

@@

\subsubsection{Proposed Algorithm}

@@

S represents the state space matrix, and A represents the action vector. R is also the reward of action. $ P (. | S, a) $ is the probability of transfer and $ \gamma \in (0,1] $ is the discount factor.  The $ \Pi (. | S) $ policy is a mapping of the state to the distribution of actions. The value-state function for state s under policy $ \Pi (. | S) $ with $ V^{\Pi} (s) $ indicates that the expected return value in state s under policy $ \Pi (. | S) ) $. The value of performing operation a in state s under the $ \Pi (. | S) $ policy is represented by $ Q ^ {\Pi} (s, a) $. We have the following relations on this basis.

@@

	V^{\Pi}(s) = \mathbb{E}_{\Pi,P}[\sum_{t=0}^{\infty}\gamma^tR_t|S_0=s]

@@

 The Q-value is as below.

@@

  $\mathbb{E}$ represented the statistical average. 
 Based on the Bellman equation we have

@@

	V^{\Pi}(s) = \mathbb{E}_{\Pi,P}[R+\gamma V^{\Pi}(s')]

@@

  	Q^{\Pi}(s,a) = \mathbb{E}_{\Pi,P}[R+\gamma Q^{\Pi}(s',a')]

@@

	T^{*}Q(s,a) = \mathbb{E}_{\Pi^*,P}[R+\gamma Q(s',a')]

@@

	Q(s_{t+1},a_{t+1}) = Q(s_t,a_t)+\alpha[ r_{t+1} + \gamma \max_{a \in A}{Q(s_{t+1},a)}-Q(s_t,a_t)]

@@

		&\textstyle  \sum_{s=1}^{S} y_{s,d}(t) \bar{\Omega}_{s}^{tot}  \leq   \tau_{d} \quad  \forall d, \forall ;  \label{eqomega}

@@

\item In this task, we want to study the O-RAN system and the challenges of it, also we want to analyze the machine learning method in the near-time RIC and non real-time RIC to find the best feasible system model and problem formulation

@@

\item Task 2: Investigate the best solution for our system model

@@

\item In this task, we want to find the best deep reinforcement learning and deep learning method for our system model. We talk a bit about it in the proposed algorithm, but we need to study more about it to find the best solution for our problem and collect the dataset for our system model.

@@

\item In this task, we want to collect a real dataset by implementing the ORAN system for a small cell with low users to obtain a dataset and compare our results with accurate results. O-RAN Alliance and Open network foundation are two different groups that implement the software of the ORAN system. I plan to implement the ORAN system on the server to obtain different datasets and face the challenges of this system. 

@@

\item In this task, we want to obtain the numerical results from different methods and compare them with each other for our paper

@@

\item Task 5: Generalized our method for other feasible system models

@@

\item In this task, we want to generalized our methods for two time scale  ORAN system models  

@@

\item In this task, we want to write and review the paper

@@

\begin{table}
 \caption {Research Plan} \label{table:1a}
 \begin{center}
  \begin{tabular}{||c c ||}
  \hline
Month & Tasks \\ [0.5ex]
  \hline\hline
  First Month & Complete the System model for the Intelligent RAN slicing\\
  \hline
  Second Month & Find the best method for this system model \\
  \hline
  Third Month & Implement the O-RAN system to collect real dataset  \\
  \hline
    Fourth Month & Obtain Numerical Results\\
  \hline
    Fifth Month & Generalized our method for other feasible ORAN system models\\
  \hline
      Sixth Month & Write and review the paper\\
  \hline
 \end{tabular}
 \end{center}
 \end{table}

>>>>

\textbf{\Large Research Plan} \\
\vspace{10mm}
\textbf{Department of Electrical and Computer Engineering}\\
\vspace{20mm}
%{\large University of Oulu}\\
{\large University of Tehran}\\
\vspace{20mm}
\end{center}
\vspace{10mm}
{\scriptsize Provisional title:}\\
Dynamic Resource Allocation in O-RAN Architecture using Network Slicing\\

@@

%{\scriptsize Supervisor name:}\\
%Dr. Onel Lopez\\
\vspace{3mm}

@@

\subsection{Main Contributions}
In this research, as depicted in Figure \ref{fig:c11}, we aim at solving the problem of dynamic network slicing in the O-RAN system. 
Here, we study a single-cell downlink situation involving multiple network slices that share existing radio sources.
The main contributions of
this research are summarized as follow:
\begin{itemize}
\item 
Here, we separate the scheduling into two-time scales. So we considered the two-time scale system and solved it in two layers. On a large time scale, the problem of obtaining an optimal number of VNFs and the VNF placement is performed. Also, the assignment of PRB to the slices is obtained. On a small-time scale, the problem of power allocation, O-RU association, and the assignment of PRB to UE in each slice is applied.
\item 
We consider three types of services that requires specific QoS: i) URLLC, which requires low latency and high reliability; ii) eMBB, which needs high data rate; and iii) mMTC, which demand short-packet connectivity support for a massive number of low-power devices.
The problem of RAN slicing for different types of services is studied in this research.

@@

In addition, there are $R$ multi-antenna RU that are shared between slices. Each RU $r \in \{1,2,...,R \}$
has $J$ antenna for transmitting and receiving data. Moreover, all RUs, have access to PRBs.
\subsection{The Achievable Rate}
The SNR of $i^{th}$ UE requesting served at slice $s$ on PRB $k$ is obtained from
\begin{equation}\label{eq2}
\rho_{r,u(s,i)}^{k} =  \frac{|p_{r,u(s,i)}^{k}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2}{BN_0 + I_{r,u(s,i)}^{k}},
\end{equation} 
where $p_{r,u(s,i)}^{k}$ represents the transmission power from O-RU $r$ to $i^{th}$ UE served at slice $s$ on PRB $k$. 
${\bold{h}_{r,u(s,i)}^{k}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
$r^{th}$ RU to the $i^{th}$ UE in $s^{th}$ slice. In addition, $\bold{w}_{r,u(s,i)}^{k} \in \mathbb{C}^{J}$ depicts the  transmit beamforming vector from $r^{th}$ RU to the $i^{th}$ UE in $s^{th}$ slice that is the zero forcing beamforming vector to minimize the interference which is indicated as below
\begin{equation}
\bold{w}_{r,u(s,i)}^{k} = {\bold{h}_{r,u(s,i)}^{k}}({\bold{h}_{r,u(s,i)}^{H \: k}} {\bold{h}_{r,u(s,i)}^{k}})^{-1}.
\end{equation}
Moreover, $g_{u(s,i)}^r \in \{0,1\}$ is a binary variable that illustrates whether RU $r$ is mapped to the $i^{th}$ UE allocated to $s^{th}$ slice or not. 
Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u(s,i)}^{k}$ is the power of interfering signals represented as follow
\begin{equation}\label{eqI}
\begin{split}
I_{r,u(s,i)}^{k} &=
 \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} \gamma_{1}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}\\
&+ \underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} \gamma_{2}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
\end{split}
\end{equation}
where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
$e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU.

@@

\mathcal{R}_{u(s_1,i)}^{e} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{e,r},

@@

\mathcal{R}_{u(s_2,i)}^{\mathfrak{u},r} &= \sum_{k=1}^{K_{s_2}} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_2,i)}^{k}){\beta}_{u(s_2,i)}^{k}, \quad \mathfrak{u} \in  \{u,m\}, \\
\mathcal{R}_{u(s_1,i)}^{\mathfrak{u}} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_2,i)}^{e,r}, 

@@

So, we assume that the total delay is approximate to the processing delay, i.e.,

@@

T^{\text{\text{tot}}} \approx T^{\text{proc}}.

@@

    \end{cases}.       

@@

\phi_{s} = M_s^u \phi_s^u + M_s^c \phi_s^c+ M_s^d \phi_s^d,

@@

\subsection{AI Approaches and Numerical Results}

@@

\subsection{AI Approaches} \label{AIP}

@@

S represents the state space matrix, and A represents the action vector. R is also the reward of action. $ P (. | S, a) $ is the probability of transfer and $ \gamma \in (0,1] $ is the discount factor.  The $ \Pi (. | S) $ policy is a mapping of the state to the distribution of actions. The value-state function for state s under policy $ \Pi (. | S) $ with $ V^{\Pi} (s) $ indicates that the expected return value in state s under policy $ \Pi (. | S) ) $. The value of performing operation a in state s under the $ \Pi (. | S) $ policy is represented by $ Q ^ {\Pi} (s, a) $. We have the following relations on this basis:

@@

	V^{\Pi}(s) = \mathbb{E}_{\Pi,P}[\sum_{t=0}^{\infty}\gamma^tR_t|S_0=s],

@@

 The Q-value is as follows

@@

 Here $\mathbb{E}$ represents the statistical average. 
 Based on the Bellman equation, we have

@@

	V^{\Pi}(s) = \mathbb{E}_{\Pi,P}[R+\gamma V^{\Pi}(s')],

@@

  	Q^{\Pi}(s,a) = \mathbb{E}_{\Pi,P}[R+\gamma Q^{\Pi}(s',a')],

@@

	T^{*}Q(s,a) = \mathbb{E}_{\Pi^*,P}[R+\gamma Q(s',a')].

@@

	Q(s_{t+1},a_{t+1}) = Q(s_t,a_t)+\alpha[ r_{t+1} + \gamma \max_{a \in A}{Q(s_{t+1},a)}-Q(s_t,a_t)],

@@

		&\textstyle  \sum_{s=1}^{S} y_{s,d}(t) \bar{\Omega}_{s}^{tot}  \leq   \tau_{d} \quad  \forall d;  \label{eqomega}

@@

\item In this task, we want to study the O-RAN system and the corresponding challenges. Also, we want to analyze the machine learning method in the near real-time RIC and non real-time RIC to find the best feasible system model and problem formulation.

@@

\item Task 2: Investigate the suitable solution for our system model

@@

\item In this task, we want to find the suitable deep reinforcement learning and deep learning methods for our system model. We have some preliminary ideas as discussed in Section \ref{AIP}, but we need to study more about it to find the best solution for our problem and collect the dataset for our system model.

@@

\item In this task, we want to collect a real dataset by implementing the ORAN system for a small cell with few users to obtain a dataset and compare our simulation results with actual results obtained from the real implementation of ORAN. O-RAN Alliance and Open network foundation are two different groups that implement the software of the ORAN system. I plan to implement the ORAN system on the server to obtain different datasets and face the challenges of this system. 

@@

\item In this task, we want to obtain the numerical results from different methods and compare them with each other for our paper.

@@

\item Task 5: Generalize our method for other feasible system models

@@

\item In this task, we want to generalize our methods for two-time scale ORAN system models.  For instance, we consider generalizing the system model with other parameters such as UE admission, priority, and reliability.  

@@

\item In this task, we want to write, review and finally submit the paper.

@@

\begin{table}
 \caption {Research Plan} \label{table:1a}
 \begin{center}
  \begin{tabular}{||c c ||}
  \hline
Month & Tasks \\ [0.5ex]
  \hline\hline
  First Month & Complete the System model for the Intelligent RAN slicing\\
  \hline
  Second Month & Find the best method for this system model \\
  \hline
  Third Month & Implement the O-RAN system to collect real dataset  \\
  \hline
    Fourth Month & Obtain Numerical Results\\
  \hline
    Fifth Month & Generalize our method for other feasible ORAN system models\\
  \hline
      Sixth Month & Write, review and finally submit the paper\\
  \hline
 \end{tabular}
 \end{center}
 \end{table}
